The X-linked intellectual disability gene KDM5C is a sex-biased brake against germline programs in somatic lineages

### 2024-09-27 submission/manuscript.Rmd
add XX vs XY GO to supplement and pvalues to text

In EpiLCs, homozygous and heterozygous _Kdm5c_ knockout females expressed over double the number of germline-enriched genes than hemizygous males (Figure 4A, Supplementary Table 3). While the majority of germline DEGs in _Kdm5c_-KO males were also dysregulated in females (74%), many were sex-specific, such as _Tktl2_ and _Esx1_ (Figure 4B). We then compared the known functions of germline genes dysregulated uniquely in males and females or misexpressed in all samples (Figure 4C, Supplementary Table 3). Female-specific germline DEGs were enriched for meiotic (GO:0051321 - meiotic cell cycle) and flagellar (GO:0003341 - cilium movement) functions, while male-specifc DEGs had roles in mitochondrial and cell signaling (GO:0070585 - protein localization to mitochondrion).

>>>>

In EpiLCs, homozygous and heterozygous _Kdm5c_ knockout females expressed over double the number of germline-enriched genes than hemizygous males (Figure 4A, Supplementary Table 3). While the majority of germline DEGs in _Kdm5c_-KO males were also dysregulated in females (74%), many were sex-specific, such as _Tktl2_ and _Esx1_ (Figure 4B). We then compared the known functions of germline genes dysregulated uniquely in males and females or misexpressed in all samples (Figure 4C, Supplementary Table 3). Female-specific germline DEGs were enriched for meiotic (GO:0051321 - meiotic cell cycle, p.adjust = 7.81E-14) and flagellar (GO:0003341 - cilium movement, p.adjust = 4.87E-06) functions, while male-specifc DEGs had roles in mitochondrial and cell signaling (GO:0070585 - protein localization to mitochondrion, p.adjust = 0.025).
